%%% Version 3.4 Generated 2022/06/14 %%%
%%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
%%% In http://www.ctan.org/ you can find the packages and how to install them, if necessary. %%%
%%%  NB logo1.jpg is required in the path in order to correctly compile front page header %%%

%\documentclass[utf8]{FrontiersinHarvard}

\documentclass[utf8]{FrontiersinVancouver} % for articles in journals

%\documentclass[utf8]{frontiersinFPHY_FAMS} % Vancouver Reference
%Style (Numbered) for articles in the journals "Frontiers in Physics"
%and "Frontiers in Applied Mathematics and Statistics"

%\setcitestyle{square} % for articles in the journals "Frontiers in Physics" and "Frontiers in Applied Mathematics and Statistics" 

\usepackage{url}
\usepackage{lineno}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}
\usepackage{subcaption}
\usepackage[onehalfspacing]{setspace}
\usepackage{comment}
\usepackage{xcolor}
\usepackage{todonotes}

\newcommand{\TODO}[1]{\todo[inline]{#1}}

\newcommand{\YES}{yes}
\makeatletter\newcommand{\tableofcontents}{\@starttoc{toc}}\makeaother

\linenumbers


\def\keyFont{\fontsize{8}{11}\helveticabold }

\def\firstAuthorLast{von Laszewski {et~al.}} 
\def\Authors{Gregor von Laszewski\,$^{1,*}$,
 J.P. Fleischer\,$^{1}$
Robert Knuuti\,$^{1}$
 and Geoffrey. C. Fox\,$^{1}$}

% Affiliations should be keyed to the author's name with superscript
% numbers and be listed as follows: Laboratory, Institute, Department,
% Organization, City, State abbreviation (USA, Canada, Australia), and
% Country (without detailed address information such as city zip codes
% or street names).

% If one of the authors has a change of address, list the new address
% below the correspondence details using a superscript symbol and use
% the same symbol to indicate the author in the author list.

\def\Address{$^{1}$
Biocomplexity Institute,
University of Virginia,
% Town Center Four,
% 994 Research Park Boulevard,
 Charlottesville, VA, 22911, USA
}

% The Corresponding Author should be marked with an asterisk Provide
% the exact contact address (this time including street name and city
% zip code) and email of the corresponding author

\def\corrAuthor{Gregor von Laszewski, Biocomplexity Institute,
University of Virginia,
Town Center Four,
994 Research Park Boulevard,
 Charlottesville, VA, 22911, USA
}

\def\corrEmail{laszewski@gmail.com}

\newcommand{\TITLE}{Insights in High-Performance Big Data Systems Gained from
  Educational
  MLCommons Earthquake Benchmarks Efforts}


\begin{document}

% outcomment toc when submitting

{\bf \TITLE}

\bigskip

\tableofcontents

\title{\TITLE}


\onecolumn
\firstpage{1}

\author[\firstAuthorLast ]{\Authors} %This field will be automatically populated
\address{} %This field will be automatically populated
\correspondance{} %This field will be automatically populated

\extraAuth{}

% If there are more than 1 corresponding author, comment this line and
%uncomment the next one.  \extraAuth{corresponding Author2
%\\ Laboratory X2, Institute X2, Department X2, Organization X2,
%Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip
%Code2, X2 Country X2, email2@uni2.edu}


\maketitle


\begin{abstract}

\section{}

\input{section-abstract}


\tiny \keyFont{ \section{Keywords:} deep learning, benchmarking, hyper
  parameter search, hybrid heterogeneous hyperparameter search,
  earthquake forecasting}

% All article types: you may provide up to 8 keywords; at least 5 are mandatory.

\end{abstract}


\section{Introduction}

todo \citep{las-22-arxiv-workflow-cc}

\citep{las-infogram}
\citep{las-workflow,las07-workflow}


% For Original Research Articles \citep{conference}, Clinical Trial
% Articles \citep{article}, and Technology Reports \citep{patent}, the
% introduction should be succinct, with no subheadings \citep{book}. For
% Case Reports the Introduction should include symptoms at presentation
% \citep{chapter}, physical exams and lab results \citep{dataset}.



\input{section-mlcommons}

\input{section-edu-ml}
\input{section-edu-mlcommons}

\input{section-earthquake}

\input{section-dev}

\input{section-data}
\input{section-workflow}
\input{section-eq-performance}

% \subsubsection{Federated Analytics Service Catalogue}
% \subsubsection{Catalogue Attributes}
% \subsubsection{Federated analytics service Registries}
% \subsubsection{Registry Attributes}

% \subsection{Resource Accessibility}
% \subsubsection{Resource Management}
% \subsubsection{Security}

% three axis graph: system, software, science

\section{Nomenclature}

\subsection{Resource Identification Initiative}

{\bf Organization:} \verb|RRID:SCR_011743|

\section*{Conflict of Interest Statement}

The authors declare that the research was conducted in the absence of
any commercial or financial relationships that could be construed as a
potential conflict of interest.

\section*{Author Contributions}

{\em GvL} is the lead author and main contributor to this paper. He
has modified and augmented the earthquake paper to include the ability
to execute hyperparameters. {\em JPF} is a student that has
contributed to various aspects of the workflow component of the paper
and to a number of executions and evaluations of experiment runs. {\em
  RK} was a student and has helped together with {\em GVL} in the
implementation of cloudmesh-sbatch and the porting of the effort to
the UVA machine.  {\em GCF} is the author of the earthquake code and
facilitates the interactions with the MLCommons Science Working group
as a group leader of that effort.

\section*{Funding}

Work was in part funded by the NSF CyberTraining: CIC: CyberTraining
for Students and Technologies from Generation Z with the award numbers
1829704 and 2200409 and NIST 60NANB21D151T.  The work was also funded
by the Department of Energy under the grant Award
No. DE-SC0023452. The work was conducted at the Biocomplexity
Institute and Initiative at University of Virginia.

\section*{Acknowledgments}

We like to thank Thomas Butler and Jake Kolessar for their
contributions during the capstone project while focusing on executing
initial runs of the code, and experimenting with modifications to the
code including logging. Please note that since this team finished
their work, significant improvements have been made by the authors of
this paper.

\section*{Data Availability Statement}

The code is all in the public domain and available on GitHub at the following locations

\begin{itemize}

\item {\bf cloudmesh-cc} -- Is a code to control workflows to be executed on
  remote computing
  resources. \url{https://github.com/cloudmesh/cloudmesh-cc}

\item {\bf cloudmesh-sbatch} -- Is a code to generate batch scripts for
  hyperparameter studies high-performance computers so they can be
  executed on different supercomputers by multiple
  accounts. \url{https://github.com/cloudmesh/cloudmesh-sbatch}

\item {\bf cloudmesh} -- Cloudmesh is a large collection of repositories for
  accessing cloud and HPC
  resources. \url{https://github.com/orgs/cloudmesh/repositories}

\item {\bf mlcommons eartchquake production code} -- The MLCommons Sceience
  Working group is described at
  \url{https://mlcommons.org/en/groups/research-science/}. This page
  contains the links to the production-level earthquake code.

\item {\bf MLcommons earthquake development code} -- The development version of
  the code is available in this repository. It also contains many of
  the analysis scripts that are not part of the production code
  hosted by MLCommons \url{https://github.com/laszewsk/mlcommons}.

\end{itemize}


% \bibliographystyle{Frontiers-Harvard}

\bibliographystyle{Frontiers-Vancouver} % Many Frontiers journals
% use the numbered referencing system, to find the style and resources
% for the journal you are submitting to:
% https://zendesk.frontiersin.org/hc/en-us/articles/360017860337-Frontiers-Reference-Styles-by-Journal

\bibliography{vonLaszewski-references}


\end{document}
